---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.align="center"
)
```

# rjdfilters

rjdfilters is R package on linear filters. 
It allows to create symmetric and asymmetric moving averages with:

- local polynomial filters, as defined by Proietti and Luati (2008);

- the FST approach  of Grun-Rehomme, Guggemos, and Ladiray (2018), based on the optimization of the three criteria Fidelity, Smoothness and Timeliness.

Some quality criteria defined by Wildi and McElroy (2019) can also be computed.

## Installation

rjdfilters relies on the [rJava](https://CRAN.R-project.org/package=rJava) package and Java SE 8 or later version is required.

```{r, eval = FALSE}
# Install development version from GitHub
# install.packages("devtools")
devtools::install_github("palatej/rjdfilters")
```

If you have troubles with the installation, check the [installation manual](https://github.com/jdemetra/rjdemetra/wiki/Installation-manual) of RJDemetra.

## Basic example


```{r plot-example, eval = TRUE}
library(rjdfilters)
y <- window(retailsa$WomensClothingStores,start = 2000)
```

## Bibliography

Grun-Rehomme, Michel, Fabien Guggemos, and Dominique Ladiray (2018). “Asymmetric Moving Averages Minimizing Phase Shift”. In: *Handbook on Seasonal Adjustment*. URL: https://ec.europa.eu/eurostat/web/products-manuals-and-guidelines/-/KS-GQ-18-001.

Proietti, Tommaso and Alessandra Luati (Dec. 2008). “Real time estimation in local polynomial regression, with application to trend-cycle analysis”. In: *Ann. Appl. Stat.* 2.4, pp. 1523–1553. DOI: 10.1214/08-AOAS195. URL: https://doi.org/10.1214/08-AOAS195.

Wildi, Marc and Tucker McElroy (2019). “The trilemma between accuracy, timeliness and smoothness in real-time signal extraction”. In: *International Journal of Forecasting* 35.3, pp. 1072–1084. URL: https://EconPapers.repec.org/RePEc:eee:intfor:v:35:y:2019:i:3:p:1072- 1084.
